%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Principal Cloud Platform Specialist} % Job title
{Dell EMC} % Organization
{Converged Platforms \& Solutions} % Location
{May 2017 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
Presales specialist focused on driving infrastructure modernization and automation, enabling customer cloud, IT, and digital transformation strategies. Focused on turnkey engineered systems that deliver outcome-based results with full-stack cloud offerings for IaaS, CaaS, and PaaS use cases. In this role I leverage a wide portfolio, including engineered systems and data protection solutions from Dell EMC, virtualization and cloud solutions from VMware and Microsoft, and application-oriented platform software from Pivotal.
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Principal Systems Engineer and Technical Evangelist} % Job title
{Dell EMC} % Organization
{MidAtlantic Enterprise Core} % Location
{Jun. 2015 - May 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
Focused on driving technology strategy and architecture for large, complex, and high profile campaigns within the MidAtlantic Enterprise area. Mentored core Systems Engineers throughout the area on new and emerging technologies like all flash, hyperconverged, software-defined, cloud, containers, and DevOps.
\end{cvitems}
}

%------------------------------------------------

\cventry
{Principal Systems Engineer} % Job title
{Dell EMC} % Organization
{Modern Infrastructure Team (MIT)} % Location
{Oct. 2012 - Jun. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
Presales Storage and Availability Specialist covering Symmetrix VMAX, XtremIO, VNX, VPLEX, RecoverPoint, and Connectrix technologies within the MidAtlantic / SouthEast / TOLA regions.
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Senior Systems Engineer} % Job title
{Dell EMC} % Organization
{Federal Strategic Accounts Core} % Location
{Jun. 2010 - Sep. 2012} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
Account Systems Engineer for Dell EMC's Federal Strategic Accounts district. Presales technical lead for the United States Postal Service (USPS). Drove account strategies and technical sales, leading to record growth and early adoption of key emerging technologies such as automated storage tiering and all flash.
\end{cvitems}
}

%------------------------------------------------

\cventry
{Advisory Solutions Architect} % Job title
{Dell EMC} % Organization
{Federal Professional Services} % Location
{Apr. 2004 - May 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Technical Lead and mentor for projects within the Army, Air Force, and Pentagon districts.}
\item {Provided subject matter expertise during presales, and developed services scope/pricing.}
\item {Designed and implemented SAN and NAS solutions to satisfy customer consolidation, business continuity, and disaster recovery needs, primarily based on the EMC Symmetrix DMX/VMAX, Clariion, and Celerra platforms with Cisco, Brocade and McData fibre channel switches.}
\item {Performed customer health and performance assessments and presentations, identifying points of concern within customers’ networked storage environment.}
\item {Promoted from Senior Solutions Architect in May 2008}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Solutions Architect} % Job title
{Novus Consulting Group} % Organization
{Acquired by IBM} % Location
{Sep. 2001 - Dec. 2003} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented networked storage products, including EMC Symmetrix and DMX, Clariion, Celerra, SRDF, TimeFinder, SnapView, MirrorView, SAN Copy, ECC, Brocade and McData directors}
\item {Created perl scripts to automate backup, disaster recovery, data migration, and data refresh processes.}
\item {Led and mentored junior level engineers in the field, and presented technical information to both customers and internal employees.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{IT Manager} % Job title
{Stitch Networks Corporation} % Organization
{Acquired by USA Technologies} % Location
{1999 - 2001} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { Responsible for all aspects of network and systems administration and data center operations.}
\item {Built and led a team of Systems Administrators and Network Engineers to ensure continual uptime of core revenue producing business applications.}
\item { Achieved maximum uptimes by deploying highly available system and network components, including multi-homed Internet connections to geographically diverse ISPs using BGP ECMP, and Sun Cluster 2.2 for Oracle Parallel Server / RAC on Solaris.}
\item { Deployed an NT/Win2k network with Exchange 5.5 to support internal infrastructure, later upgrading to Windows 2000 with Active Directory and moving file serving from NT to Network Appliance.}
\item { Automated production and development processes using Perl and shell scripts.}
\item { Presented major accomplishments, milestones, and potential future projects to company board of directors.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Systems Engineer} % Job title
{JVC Technologies} % Organization
{Plymouth Meeting, PA} % Location
{1998 - 1999} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { Involved in both pre-sales and post-sales technical consulting projects.}
\item { Performed on-site installation, consulting, and support for clients with mixed networking environments, concentrating primarily on Sun Microsystems solutions.}
\item { Recommended, designed, and implemented security solutions for clients, including firewalls, VPNs, and security audits.}
\item { Designed and implemented highly available services on Solaris and Citrix Metaframe platforms.}
\item { Projects ranging from short-term installations to longer-term server support and system administration.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Systems Administrator} % Job title
{PDC Solutions, Inc.} % Organization
{Acquired by Legato, then Dell EMC} % Location
{1997 - 1998} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { Support and administration of heterogeneous mostly Sun LAN/WAN environment.}
\item { End user support of Sun workstations and PC laptop/desktops.}
\item { Administration of Citrix Winframe \& Metaframe servers housing Sales database clients. Back end on Sun running Oracle.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Intern} % Job title
{MicroAge of Exton} % Organization
{Exton, PA} % Location
{1995 - 1997} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { Administration and support of Novell, Windows, SCO UNIX, Linux, and Citrix network environment.}
\item { Planned and implemented corporate TCP/IP rollout, Checkpoint Firewall-1 installation, and Linux-based mail solution.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Intern} % Job title
{PDC Solutions, Inc.} % Organization
{King of Prussia, PA} % Location
{1994 - 1995} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { Administration and support for SunOS 4.1.x and Solaris 2.5.1 workstations and servers.}
\end{cvitems}
}

%------------------------------------------------
\end{cventries}